Where and How Do Models Fail? A Visual Exploration Tool for Analyzing and Interpreting Natural Language Inference

### 2018-03-20 paper/intro.tex
fix sentences refresh
update abstract

% (What is the high level motivation)
% What is the obsatcle for effectively apply machine learning model
With the recent advances in neural network based model, machine learning has
gained unprecedented popularity, and its adaption permeated many fields of studies.
%
However, from researchers to practitioners, one often need to overcome many
obstacles during the training, debugging, and tuning processes to unleash
the full potential of these models.
%
Identify where and how does the error occur and come up with hypothesis for
why does the model fail is critical to the design and application of various models.
%quickly identify where the errors are
However, providing meaningful answers to these questions is an extremely challenging task.
% Naturally the identification of failure scenarios is an essential first step in diagnosing procedure.
%the potential limitation of the test dataset
On the one hand, recognize where the model fail is non trivial. The standard evaluation approach provides limited information. i.e., the performance number (e.g., prediction accuracy on the test set) alone cannot answer many important questions in the model diagnostic process, such as what the often made mistakes are, and how sensitive are the model concerning small perturbation in the input, etc. On the other hand, infer why the model fails is challenging as well (i.e., models are often referred to as black boxes),
which require the ability to peek inside the model and understand the relationship between the
model input, critical internal mechanisms, as well the output predictions.

%%%%%%%%% accessing internal states are important %%%%%%%%%%%%
The wide application of machine learning models also call for increasing demands for model accountability (e.g., what is the evidence for making the decision) and model fairness (e.g., is the prediction affected by the bias in the training data).
% Making sense and explaining predictions made by neural networks is also becoming a necessity.
%
Many works~\cite{RibeiroSinghGuestrin2016} have been dedicated to providing intuitive explanations for a given prediction, several of which approach the problem from a model agnostic approach that made them applicable to different applications (i.e., by fitting a simplier linear model near the prediction of interests).
%
Despite being invaluable for the providing human understandable explaination, the lack of the ability to access and explore the internal states of the model, which is vitally important to make sense of why a model fail, limits their ability for more in depth exploration and evaluation of the model.

>>>>

% (What is the high level motivation)
% What is the obsatcle for effectively apply machine learning model
With the recent advances in neural network based model, machine learning has
gained unprecedented popularity, and its adaption permeated many fields of studies.
%
However, from researchers to practitioners, one often need to overcome many
obstacles during the training, debugging, and tuning processes to unleash
the full potential of these models.
%
Identify where and how does the error occur and come up with hypothesis for
why does the model fail is critical to the design and application of various models.
%quickly identify where the errors are
However, providing meaningful answers to these questions is an extremely challenging task.
% Naturally the identification of failure scenarios is an essential first step in diagnosing procedure.
%the potential limitation of the test dataset
On the one hand, recognize where the model fail is non-trivial. The standard evaluation approach (i.e., the prediction accuracy on the test set) provides limited information and cannot answer many important questions that are essential to the model diagnostic process. Questions such as, how stable predictions are concerning small perturbation in the input, how these predictions arrive (i.e., the model may come up with the correct prediction by pickup unintended feature/alignment), and what are the often made mistakes, are all essential in systematic examination and evaluation of the model. On the other hand, infer why the model fails is even more challenging. Since neural network models are often referred to as black boxes, hypothesizing what happened in prediction process require the ability to peek inside the model and understand the intricate relationships between model inputs, critical internal mechanisms, as well the output predictions.

\begin{itemize}
    \item Study the classifier  vs. single instance evaluation
    \item Model agnostic vs. reveal intern states
    \item View model as invariant object vs. interrogate the model via partial/full updates
\end{itemize}

%%%%%%%%% accessing internal states are important %%%%%%%%%%%%
To analyzing the
Many method has been

The wide application of machine learning models also call for increasing demands for model accountability (e.g., what is the evidence for making the decision) and model fairness (e.g., is the prediction affected by the bias in the training data).
% Making sense and explaining predictions made by neural networks is also becoming a necessity.
%
Many works~\cite{RibeiroSinghGuestrin2016} have been dedicated to providing intuitive explanations for a given prediction, several of which approach the problem from a model agnostic approach that made them applicable to different applications (i.e., by fitting a simplier linear model near the prediction of interests).
%
Despite being invaluable for the providing human understandable explaination, the lack of the ability to access and explore the internal states of the model, which is vitally important to make sense of why a model fail, limits their ability for more in depth exploration and evaluation of the model.

### 2018-03-20 paper/paper_entailVis.tex
update attention is more or less working
update abstract

%% Paper title.
\title{How Do Models Fail? A Visual Exploration Tool for Analyzing and Interpreting Natural Language Inference}
%% This is how authors are specified in the journal style

@@

%% Abstract section.
% What are we doing in this paper
\abstract{
With the recent advances in deep learning, neural network based models have reset the state-of-the-art performance for nearly all linguistic tasks in natural language processing. The disruptive progress also brings enormous challenges.
The opaque nature of neural network model leads to hard to debug system and difficult to interpret mechanisms. In this work, we use textual entailment task as an example to illustrate how a flexible visualization system can not only help NLP researchers quickly identify the potential limitation of a model, but also facilitate the interpretation the model mechanisms by allowing interactive exploration of the interplay between model input, model inner states, and the prediction.
} % end of abstract

>>>>

%% Paper title.
\title{Where and How Do Models Fail? A Visual Exploration Tool for Analyzing and Interpreting Natural Language Inference}
%% This is how authors are specified in the journal style

@@

%% Abstract section.
% What are we doing in this paper
\abstract{
With the recent advances in deep learning, neural network based models have obtained the state-of-the-art performance for many linguistic tasks in natural language processing. The disruptive progress also brings enormous challenges.
The opaque nature of neural network model leads to hard to debug system and difficult to interpret mechanisms. In this work, we use natural language inference task as an example to illustrate how a flexible visualization system can not only help NLP researchers quickly identify the potential limitation of a model, but also facilitate the interpretation the model mechanisms by allowing interactive exploration of the interplay between model input, model inner states, and the prediction.
} % end of abstract
